\documentclass[9pt]{sigplanconf}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{latexsym}
\usepackage{textcomp}
\usepackage{amsfonts}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{float}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{etoolbox}

%% Patch the copyright box to make it go away.
%% Better: challenge the notion of copyright at all, put something about how
%% ACH believes that copyright is theft.
%% An interesting anecdote: the style file that has the ACM copyright notice is
%% CC-BY.
\makeatletter
\patchcmd{\maketitle}{\@copyrightspace}{}{}{}
\makeatother

\begin{document}

\title{Fandomized Algorithms and Fandom Number Generation}

\authorinfo{Lindsey Kuper \and Alex Rudnick}
           {School of Transformative Works, Indiana University}
           {\{lkuper, alexr\}@cs.indiana.edu}

\maketitle

\begin{abstract}
We introduce the concept of \emph{fandomness} and of fandomized algorithms, and
demonstrate their application in a practical fandom number generator.
\end{abstract}

\section{Introduction}

fandom variable
fandom number
fentropy
fandomized algorithm
MLP-hard
fandomly
fentropic
fenergy (?)
Dreamwidth
OTPs

\section{Fandomness and fandom variables}

A \emph{fandom variable} can take on a \emph{fandom number}, but the
generation of fandom numbers requires a source of
\emph{fentropy}. Thankfully, there exist fentropic processes in nature

\section{A practical fandom number generator}
We have developed a practical algorithm and implementation for
generating fandom numbers, a key component for any fandomized
algorithm. A naturally occurring source of fentropy, Archive of Our
Own\footnote{Google for ``archive of our own"; do you not know how to
  do web searches?\footnotemark}
\footnotetext{Oh, fine.  It's \cite{ao3}.}, supplies an
ever-increasing amount of fandomness, certainly more than the current
global demand for fentropy to power fandomized algorithms. As
fandomized algorithms become more broadly deployed, further sources of
fandomness may be required -- we may have to mine THE DARK
SOCIAL\footnote{THE DARK SOCIAL} -- but we will burn that bridge when
we get to it.

Right. Yes.

\begin{lstlisting}
lkuper@mitzi:~/repos/fandomized-algorithms/src$ ./fandom_number_generator.py 
YOUR FANDOM NUMBER: 31
from fanwork #413565 at http://archiveofourown.org/works/413565?view_adult=true
lkuper@mitzi:~/repos/fandomized-algorithms/src$ ./fandom_number_generator.py 
No numbers in fanwork #574736
No numbers in fanwork #107375
No numbers in fanwork #241151
YOUR FANDOM NUMBER: 33
from fanwork #64813 at http://archiveofourown.org/works/64813?view_adult=true
lkuper@mitzi:~/repos/fandomized-algorithms/src$ ./fandom_number_generator.py 
No numbers in fanwork #66860
No numbers in fanwork #127716
No numbers in fanwork #78820
No numbers in fanwork #127598
YOUR FANDOM NUMBER: 2
from fanwork #408282 at http://archiveofourown.org/works/408282?view_adult=true
\end{lstlisting}

\section{OTPs}

OTPs are one of the most important applications of fandom numbers.  An
OTP is when you put a character together with another character from a
secret fandom pad, the one with whom it truly belongs (mod 26).  The
true love of an OTP has been proven to be impossible to break.

\section{Markov fandom fields}

We may also wish to do inference over communities of interacting
fandom variables using a Markov fandom field via \emph{headcanon
  propagation}, although it is MLP-hard in most cases.  However, we
can perform approximate inference with loopy headcanon propagation.
Fandom-wanking is not guaranteed to terminate in this case, and a
consistent community-wide headcanon may not emerge.\footnote{The alert
  reader may have noticed that Tumblr is a platform for
  human computation \cite{luisvonahn}, performing loopy
  headcanon propagation at scale. Most Tumblr traffic is used for
  applications in protein folding and computational geology.}



%% Our practical fandom number generator downloads a pseudo-fandomly-selected
%% transformative work from AOOO, locates all of the base-10 numbers in it, and
%% then returns one of them at fandom. If for some reason there are no fandom
%% numbers present in a given transformative work, we simply try the next
%% transformative work until we find one.
%% %% XXX: alexr doesn't really like this sentence
%% (These numbers, having been used by fannish domain experts in a transformative
%% work on AO3, are guaranteed by definition to have high fentropy.)

%% This work would not be canon without the public availability of sources of
%% fentropy; the open publishing and reuse rights of the transformative works on
%% AO3 enable us to produce our own transformative works. Of course, we could use
%% a different source of fentropy, such as the AO3 splinter site arXiv, which is
%% popular for for Physics, also known as the neutrino fandom.

%% \section{Further Applications of Fandomized Algorithms}

%% \subsection{OTPs}



%% \section{Fentropy}

%% Fentropy is a measure of the fannishness of a fandom variable. Computing the
%% fentropy of a fandom variable exactly is in general MLP-Hard, although
%% approximations are possible.

%% The world's technological capacity to store and communicate fentropic
%% information has increased since the advent of the information age,
%% especially since Dreamwidth launched.

%% Unfortunately, if fentropy increases until all fenergy is equally
%% distributed, it will eventually cause the heat death of the Jossverse.

%% \section{Outro}

%% As the dictum about software development goes, ``shipping code
%% wins". We have accepted this idea as headcanon, but we realize that
%% many in the computer science community remain squicked by it.

%% As such, we wish to provide a survey of the current work in fandomized
%% algorithms and the associated formalisms; in upcoming seasons, we expect that
%% it will be revealed that fandom and computer science are the OTP.

%% Introduce the notion of \emph{fandomness} ...

\bibliographystyle{abbrvnat}
\bibliography{fandomized}

\end{document}
